Translation Elicitation: Report

### 2022-04-27 docs/index.Rmd
No idea what changed

```{r stimuli-pthn, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  left_join(
    count(
      ., 
      test_language, 
      name = "n_total"
    )
  ) %>% 
  mutate(
    test_language = paste0(
      test_language, 
      " (N = ", 
      n_total, 
      ")"
    )
  ) %>% 
  count(
    test_language, 
    pthn
  ) %>% 
  ggplot() +
  aes(
    reorder(as.factor(pthn), -n), 
    n,
    fill = test_language
  ) +
facet_wrap(
  ~test_language,
  ncol = 1
) +
  geom_col(position = position_dodge()) +
  labs(
    x = "# Phonological neighbours with higher lexical frequency\nExtracted from CLEARPOND database",
    y = "# trials",
    fill = "Test language"
  ) +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_line(
      colour = "grey", 
      linetype = "dotted"
    )
  )

@@

* fit_0: `~ 1 + (1 | participant) + (1 | word)`
* fit_1: `~ 1 + frequency_zipf + (1 + frequency_zipf | participant) + (1 | word)`
* fit_2: `~ 1 + frequency_zipf + pthn + (1 + frequency_zipf + pthn | participant) + (1 | word)`
* fit_3: `~ 1 + frequency_zipf + pthn + lv + (1 + frequency_zipf + pthn + lv | participant) + (1 | word)`
* fit_4: `~ 1 + frequency_zipf + pthn + lv + pthn:lv + (1 + frequency_zipf + pthn + pthn:lv + lv | participant) + (1 | word)`
* fit_5: `~ 1 + frequency_zipf + pthn + lv + pthn:lv + group + (1 + frequency_zipf + pthn + pthn:lv + lv | participant) + (1 | word)`
* fit_6: `~ 1 + frequency_zipf + pthn + lv + pthn:lv + group + group:lv + (1 + frequency_zipf + pthn + pthn:lv + lv | participant) + (1 | word)`

@@

coefs <- fixef(fit_6) %>% 
  as.data.frame() %>% 
  rownames_to_column("variable") %>% 
  clean_names() %>% 
  mutate_at(
    vars(estimate:q97_5), 
    ~ifelse(
      variable=="Intercept",
      inv_logit_scaled(.),
      ./4
    )
  )

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf_std" = "Frequency\n[+1 SD]",
  "pthn_std:lv_std" = "PTHN \u00d7 Levenshtein", 
  "lv_std:group1" = "Levenshtein \u00d7 Group 1",
  "lv_std:group2" = "Levenshtein \u00d7 Group 2",
  "lv_std" = "Levenshtein\n[+1 SD]",
  "pthn_std" = "PTHN\n[+1 SD]",
  "group1" =  "Group 1\n[*-ENG vs. cat-SPA]",
  "group2" = "Group 2\n[cat-ENG vs. spa-ENG]"
)

coefs %>% 
  mutate(
    variable = str_remove(variable, "b_") %>% 
      str_replace_all(str_repl) %>%  
      factor(
        levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein",
          "Group 1\n[cat/spa-ENG vs. cat-SPA]",
          "Group 2\n[cat-ENG vs. spa-ENG]",
          "Levenshtein \u00d7 Group 1",
          "Levenshtein \u00d7 Group 2"
        )
      )
  ) %>% 
  select(-est_error) %>% 
  gt() %>% 
  fmt_percent(2:4) %>% 
  cols_merge(
    c("q2_5", "q97_5"), 
    pattern = "[{1}, {2}]"
  ) %>% 
  cols_label(
    variable = md("**Predictor**"),
    estimate = md("**Mean**"),
    q2_5 = md("**95\\% CrI**"),
  ) %>% 
  tab_source_note(
    "Estimated posterior distributions of coefficients in Model 6. A\\) Population-level effects. Distributions indicate the estimated posterior likelihood density of regression coefficients of fixed effects. Credible intervals (*CrI*), represented with increasingly lighter segmentents in the distribution indicate the range of values that contain the true value with 95\\%, 80\\%, and 50\\% probability. Black dots represent the mean of each distribution."
  ) %>% 
  cols_align(align = "left") %>% 
  as_raw_html()
```

@@

coefs <- fixef(fit_6) %>% 
  as.data.frame() %>% 
  rownames_to_column("variable") %>% 
  clean_names() %>% 
  mutate_at(
    vars(estimate:q97_5), 
    ~ifelse(
      variable=="Intercept", 
      inv_logit_scaled(.), 
      ./4
    )
  ) %>% 
  group_split(variable) %>% 
  set_names(make_clean_names(map(., "variable"))) %>% 
  map(select, -variable) %>% 
  map(unlist)

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf_std" = "Frequency\n[+1 SD]",
  "pthn_std:lv_std" = "PTHN \u00d7 Levenshtein", 
  "lv_std:groupENGvs.SPA" = "Levenshtein \u00d7 Group 1",
  "lv_std:groupENGMCATvs.ENGMSPA" = "Levenshtein \u00d7 Group 2",
  "lv_std" = "Levenshtein\n[+1 SD]",
  "pthn_std" = "PTHN\n[+1 SD]",
  "groupENGvs.SPA" =  "Group 1\n[*-ENG vs. cat-SPA]",
  "groupENGMCATvs.ENGMSPA" = "Group 2\n[cat-ENG vs. spa-ENG]"
)

@@

# SD of random effects
post_sd_data <- posterior_draws_fixed %>% 
  filter(
    str_detect(.variable, "sd_")
  ) %>% 
  mutate(
    .variable_name = str_remove(
      .variable, 
      "sd_participant__|sd_word__"
    ) %>% 
      str_replace_all(str_repl) %>% 
      factor(
        levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein",
          "Group 1\n[cat/spa-ENG vs. cat-SPA]",
          "Group 2\n[cat-ENG vs. spa-ENG]",
          "Levenshtein \u00d7 Group 1",
          "Levenshtein \u00d7 Group 2"
        )
      ),
    group = case_when(
      str_detect(.variable, "participant") ~ "Participants",
      str_detect(.variable, "word") ~ "Words"
    ),
    .value = ifelse(
      str_detect(.variable, "Intercept"),
      inv_logit_scaled(.value),
      .value/4
    )
  )

post_sd <- filter(post_sd_data, group=="Participants") %>% 
  ggplot() +
  aes(
    .value,
    fct_rev(.variable_name)
  ) +
  stat_slab(
    aes(fill = stat(
      cut_cdf_qi(
        cdf, 
        .width = c(.5, .8, .95),
        labels = percent_format()
      )
    )
    )
  ) +
  stat_pointinterval(
    .width = 0,
    point_size = 1
  ) +
  scale_fill_manual(
    values = c("#ff2976", "#f2a7c2", "#fcd9e6"),
    na.translate = FALSE
  ) +
  scale_x_continuous(
    labels = percent,
    limits = c(0, 1)
  ) +
  labs(
    x = "SDs in P(Correct)",
    title = "By participant", 
    fill = "CrI"
  ) +
  theme(axis.text.x = element_blank()) +

  post_sd_data %>% 
  filter(group=="Words") %>% 
  ggplot() +
  aes(
    .value, 
    fct_rev(.variable_name)
  ) +
  stat_slab(
    aes(fill = stat(
      cut_cdf_qi(
        cdf, 
        .width = c(.5, .8, .95),
        labels = percent_format()
      )
    )
    )
  ) +
  stat_pointinterval(
    .width = 0, 
    point_size = 1
  ) +
  scale_x_continuous(
    labels = percent, 
    limits = c(0, 1)
  ) +
  labs(
    x = "SDs in P(Correct)",
    title = "By item", 
    fill = "CrI"
  ) +

  plot_layout(
    ncol = 1, 
    heights = c(0.85, 0.15), 
    guides = "collect"
  ) &
  theme(
    legend.position = "none",
    axis.text.y = element_text(hjust = 1),
    axis.title.x = element_blank(),
    legend.direction = "vertical",
    axis.title.y = element_blank(),
    legend.background = element_rect(fill = "grey95"),
    legend.key.height = unit(0.1, "cm"),
    legend.key = element_rect(fill = "grey95", colour = "grey95"),
    legend.text = element_text(size = 7),
    axis.ticks.y = element_blank(),
    panel.grid.major.y = element_line(
      colour = "grey",
      size = 0.5
      )
  )

# Pearson correlations between random effects
corr_mat <- VarCorr(fit_6, summary = TRUE)$participant$cor 
corr_names <- rownames(VarCorr(fit_6, summary = TRUE)$participant$cor)

@@

post_cors <- corr_data %>% 
  mutate(
    term1 = factor(
      term1,
      levels = names(str_repl), 
      ordered = TRUE
    ),
    term2 = factor(
      term2,
      levels = names(str_repl),
      ordered = TRUE
    )
  ) %>% 
  mutate_at(
    vars(term1, term2), 
    str_replace_all, 
    str_repl
  ) %>% 
  mutate(
    .value_label = case_when(
      term1==term2 ~ NA_character_,
      TRUE ~ printnum(.value, gt1 = FALSE)
    ),
    .value = case_when(
      term1==term2 ~ NA_real_,
      TRUE ~ .value
    )
  ) %>% 
  filter(
    term1 != "PTHN × Levenshtein", 
    term2 != "Intercept"
  ) %>% 
  ggplot() +
  aes(
    fct_inorder(term1), 
    fct_rev(fct_inorder(term2)),
    fill = .value
  )
geom_tile(na.rm = TRUE) +
  geom_text(
    aes(label = .value_label), 
    size = 3, 
    na.rm = TRUE
  ) +
  labs(
    x = "Term 1", 
    y = "Term 2", 
    fill = "Posterior\ncorrelation"
  ) +
  scale_fill_gradient2(
    low = "#04bf78", 
    mid = "white", 
    high = "#FFC20A", 
    na.value = "white", 
    limits = c(-0.4, 0.4)
  ) +
  scale_x_discrete(position = "top") +
  coord_equal() +
  theme(
    legend.position = c(1, 1),
    legend.direction = "horizontal",
    legend.key.height = unit(0.1, "cm"),
    legend.key.width = unit(0.3, "cm"),
    legend.justification = c(1, 1),
    legend.title = element_blank(),
    legend.text = element_text(size = 5),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 6, angle = 90, hjust = 0, vjust = 1),
    axis.text.y = element_text(size = 6, vjust = 1, hjust = 1)
  )

@@

```{r post_re_participant, echo=FALSE, fig.height=6, fig.width=9, message=FALSE, warning=FALSE, paged.print=FALSE}
post_re <- posterior_draws_random$participants %>% 
  mean_qi() %>% 
  ungroup() %>% 
  left_join(
    select(
      participants,
      participant,
      group
    )
  ) %>% 
  arrange(
    group, 
    participant, 
    .param
  ) %>% 
  mutate(
    .param_name = str_replace_all(
      .param, 
      str_repl
    ) %>%  
      factor(
        levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein",
          "Group 1\n[cat/spa-ENG vs. cat-SPA]",
          "Group 2\n[cat-ENG vs. spa-ENG]",
          "Levenshtein \u00d7 Group 1",
          "Levenshtein \u00d7 Group 2"
        )
      )
  )

ggplot(
  post_re, 
  aes(
    .value, 
    sort(as.factor(participant)), 
    xmin = .lower,
    xmax = .upper,
    colour = group
  )
) +
  facet_grid(
    group~.param_name,
    scales = "free"
  ) +
  geom_vline(
    xintercept = 0, 
    colour = "grey"
  ) +
  geom_errorbarh(
    height = 0,
    alpha = 0.75
  ) +
  geom_point(
    size = 0.1,
    shape = 4
  ) +
  labs(
    x = "Participant-level adjustment",
    y = "Participant", 
    colour = "Group",
    title = "By participant"
  ) +
  scale_color_manual(
    values = c("#1A85FF", "#ff2976", "#FFC20A"),
    na.translate = FALSE
  ) &
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    panel.grid.major.x = element_line(
      colour = "grey",
      linetype = "dotted"
    ),
    axis.text.x = element_text(size = 7),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  )
```

```{r post_re_word, echo=FALSE, fig.height=9, fig.width=7, message=FALSE, warning=FALSE, paged.print=FALSE}
fixed_intercept <- fixef(fit_6)[1,c(1, 3, 4)] %>% 
  inv_logit_scaled()

post_re <- posterior_draws_random$words   %>% 
  ungroup() %>% 
  arrange(
    word, 
    .param
  ) %>% 
  mutate(
    .param_name = str_replace_all(
      .param, 
      str_repl
    ) %>%  
      factor(
        levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein",
          "Group 1\n[cat/spa-ENG vs. cat-SPA]",
          "Group 2\n[cat-ENG vs. spa-ENG]",
          "Levenshtein \u00d7 Group 1",
          "Levenshtein \u00d7 Group 2"
        )
      ),
    .value = inv_logit_scaled(.value)
  )

ggplot(
  post_re,
  aes(
    .value,
    reorder(
      as.factor(word), 
      .value
    )
  )
) +
  geom_vline(
    xintercept = fixed_intercept[1],
    colour = "grey", 
    size = 1
  ) +

  stat_interval(
    size = 1.5,
    .width = c(0.5, 0.67, 0.95)
  ) +
  annotate(
    geom = "text",
    x = 0.7,
    y = 100,
    size = 3,
    hjust = 0.5,
    label = "Item accuracy \n(95%, 67%, and 50% CrI \nof item-level intercepts)"
  ) +
  annotate(
    geom = "rect",
    alpha = 0.15,
    xmin = fixed_intercept[2],
    xmax = fixed_intercept[3],
    ymin = -Inf,
    ymax = Inf
  ) +
  annotate(
    x = 0.7,
    xend = 0.6,
    y = 108,
    yend = 130,
    geom = "curve",
    curvature = 0.25,
    arrow = arrow(length = unit(0.2, "cm"))
  ) +
  annotate(
    geom = "text",
    x = 0.8,
    y = 10,
    size = 3,
    hjust = 0.5,
    label = "Global posterior accuracy\n(Mean ± 95% CrI of the \npopulation-level intercept)"
  ) +
  annotate(
    x = 0.7,
    xend = fixed_intercept[1]+0.05,
    y = 17,
    yend = 30,
    geom = "curve",
    curvature = 0.2,
    arrow = arrow(length = unit(0.2, "cm"))
  ) +
  labs(
    x = "Posterior probability of correct response",
    y = "Item",
    colour = "Credible Interval (CrI)",
    caption = "Credible intervals cover the range of values of the sampling space that \ncontain the true value with a given certainty."
  ) +
  scale_color_manual(
    values = c("#d2e5fc", "#9ccaff", "#1A85FF"),
    na.translate = FALSE, 
    labels = paste0(c(95, 67, 50), "%")
  ) +
  scale_x_continuous(limits = c(0, 1), labels = percent) +
  theme(
    legend.position = c(0.1, 0.9),
    legend.direction = "vertical",
    legend.justification = "left",
    legend.key = element_rect(
      fill = NA, 
      colour = NA
    ),
    panel.grid.major.x = element_line(
      colour = "grey", 
      linetype = "dotted"
    ),
    axis.text.x = element_text(size = 7),
    axis.text.y = element_text(size = 5, hjust = 1),
    axis.ticks = element_blank(),
    axis.title = element_text(size = 10),
    plot.caption.position = "plot",
    plot.caption = element_text(
      size = 9, 
      hjust = 0, 
      face = "plain",
      margin = margin(t = unit(3, "cm"))
    )
  )

ggsave(
  here("img", "accuracy.png"), 
  height = 9,
  width = 5, 
  dpi = 500
)
```

```{r post_re_word_empirical, echo=FALSE, fig.height=9, fig.width=7, message=FALSE, warning=FALSE, paged.print=FALSE}

means <- responses %>% 
  group_by(group) %>% 
  summarise(
    successes = sum(correct, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    prop = prop_adj(successes, n),
    prop_se = prop_adj_se(successes, n)
  )

posterior_accuracy <-

>>>>

```{r stimuli-pthn, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  left_join(
    count(
      ., 
      group, 
      name = "n_total"
    )
  ) %>% 
  mutate(
    test_language = paste0(
      group, 
      " (N = ", 
      n_total, 
      ")"
    )
  ) %>% 
  count(
    group, 
    pthn
  ) %>% 
  ggplot() +
  aes(
    as.factor(pthn), 
    n,
    fill = group
  ) +
  facet_wrap(
    ~group,
    ncol = 1
  ) +
  geom_col(position = position_dodge()) +
  labs(
    x = "# Phonological neighbours with higher lexical frequency\nExtracted from CLEARPOND database",
    y = "# trials",
    fill = "Test language"
  ) +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_line(
      colour = "grey", 
      linetype = "dotted"
    )
  )

@@

* fit_0: `~ 1 + (1 | participant_id) + (1 | translation_id)`
* fit_1: `~ 1 + frequency_zipf + (1 + frequency_zipf | participant_id) + (1 | translation_id)`
* fit_2: `~ 1 + frequency_zipf + pthn + (1 + frequency_zipf + pthn | participant_id) + (1 | translation_id)`
* fit_3: `~ 1 + frequency_zipf + pthn + lv + (1 + frequency_zipf + pthn + lv | participant_id) + (1 | translation_id)`
* fit_4: `~ 1 + frequency_zipf + pthn + lv + pthn:lv + (1 + frequency_zipf + pthn + pthn:lv + lv | participant_id) + (1 | translation_id)`

@@

coefs <- fixef(fit_4) %>% 
  as.data.frame() %>% 
  rownames_to_column("variable") %>% 
  clean_names() %>% 
  mutate_at(
    vars(estimate:q97_5), 
    ~ifelse(
      variable=="Intercept",
      inv_logit_scaled(.),
      ./4
    )
  )

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf_std" = "Frequency\n[+1 SD]",
  "pthn_std:lv_std" = "PTHN \u00d7 Levenshtein", 
  "lv_std" = "Levenshtein\n[+1 SD]",
  "pthn_std" = "PTHN\n[+1 SD]"
)

coefs %>% 
  mutate(
    variable = str_remove(variable, "b_") %>% 
      str_replace_all(str_repl) %>%  
      factor(
        levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein"
        )
      )
  ) %>% 
  select(-est_error) %>% 
  gt() %>% 
  fmt_percent(2:4) %>% 
  cols_merge(
    c("q2_5", "q97_5"), 
    pattern = "[{1}, {2}]"
  ) %>% 
  cols_label(
    variable = md("**Predictor**"),
    estimate = md("**Mean**"),
    q2_5 = md("**95\\% CrI**"),
  ) %>% 
  tab_source_note(
    "Estimated posterior distributions of coefficients in Model 6. A\\) Population-level effects. Distributions indicate the estimated posterior likelihood density of regression coefficients of fixed effects. Credible intervals (*CrI*), represented with increasingly lighter segmentents in the distribution indicate the range of values that contain the true value with 95\\%, 80\\%, and 50\\% probability. Black dots represent the mean of each distribution."
  ) %>% 
  cols_align(align = "left") %>% 
  as_raw_html()
```

@@

coefs <- fixef(fit_4) %>% 
  as.data.frame() %>% 
  rownames_to_column("variable") %>% 
  clean_names() %>% 
  mutate_at(
    vars(estimate:q97_5), 
    ~ifelse(
      variable=="Intercept", 
      inv_logit_scaled(.), 
      ./4
    )
  ) %>% 
  group_split(variable) %>% 
  set_names(make_clean_names(map(., "variable"))) %>% 
  map(select, -variable) %>% 
  map(unlist)

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf_std" = "Frequency\n[+1 SD]",
  "pthn_std:lv_std" = "PTHN \u00d7 Levenshtein", 
  "lv_std" = "Levenshtein\n[+1 SD]",
  "pthn_std" = "PTHN\n[+1 SD]"
)

@@

# SD of random effects
post_sd_data <- posterior_draws_fixed %>% 
  filter(
    str_detect(.variable, "sd_")
  ) %>% 
  mutate(
    .variable_name = str_remove(
      .variable, 
      "sd_participant_id__|sd_translation_id__"
    ) %>% 
      str_replace_all(str_repl) %>% 
      factor(
        levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein"
        )
      ),
    group = case_when(
      str_detect(.variable, "participant") ~ "Participants",
      str_detect(.variable, "translation") ~ "Words"
    ),
    .value = ifelse(
      str_detect(.variable, "Intercept"),
      inv_logit_scaled(.value),
      .value/4
    )
  )

post_sd <- post_sd_data %>% 
  filter(group=="Participants") %>% 
  ggplot() +
  aes(
    .value,
    fct_rev(.variable_name)
  ) +
  stat_slab(
    aes(fill = stat(
      cut_cdf_qi(
        cdf, 
        .width = c(.5, .8, .95),
        labels = percent_format()
      )
    )
    )
  ) +
  stat_pointinterval(
    .width = 0,
    point_size = 1
  ) +
  scale_fill_manual(
    values = c("#ff2976", "#f2a7c2", "#fcd9e6"),
    na.translate = FALSE
  ) +
  scale_x_continuous(
    labels = percent,
    limits = c(0, 1)
  ) +
  labs(
    x = "SDs in P(Correct)",
    title = "By participant", 
    fill = "CrI"
  ) +
  theme(axis.text.x = element_blank()) +

  post_sd_data %>% 
  filter(group=="Words") %>% 
  ggplot() +
  aes(
    .value, 
    fct_rev(.variable_name)
  ) +
  stat_slab(
    aes(
      fill = stat(
        cut_cdf_qi(
          cdf, 
          .width = c(.5, .8, .95),
          labels = percent_format()
        )
      )
    )
  ) +
  stat_pointinterval(
    .width = 0, 
    point_size = 1
  ) +
  scale_x_continuous(
    labels = percent, 
    limits = c(0, 1)
  ) +
  labs(
    x = "SDs in P(Correct)",
    title = "By item", 
    fill = "CrI"
  ) +
  plot_layout(
    ncol = 1, 
    heights = c(0.85, 0.15), 
    guides = "collect"
  ) &
  theme(
    legend.position = "none",
    axis.text.y = element_text(hjust = 1),
    axis.title.x = element_blank(),
    legend.direction = "vertical",
    axis.title.y = element_blank(),
    legend.background = element_rect(fill = "grey95"),
    legend.key.height = unit(0.1, "cm"),
    legend.key = element_rect(fill = "grey95", colour = "grey95"),
    legend.text = element_text(size = 7),
    axis.ticks.y = element_blank(),
    panel.grid.major.y = element_line(
      colour = "grey",
      size = 0.5
    )
  )

# Pearson correlations between random effects
corr_mat <- VarCorr(fit_4, summary = TRUE)$participant_id$cor 
corr_names <- rownames(VarCorr(fit_4, summary = TRUE)$participant_id$cor)

@@

post_cors <- corr_data %>% 
  mutate(
    term1 = factor(
      term1,
      levels = names(str_repl), 
      ordered = TRUE
    ),
    term2 = factor(
      term2,
      levels = names(str_repl),
      ordered = TRUE
    )
  ) %>% 
  mutate_at(
    vars(term1, term2), 
    str_replace_all, 
    str_repl
  ) %>% 
  mutate(
    .value_label = case_when(
      term1==term2 ~ NA_character_,
      TRUE ~ printnum(.value, gt1 = FALSE)
    ),
    .value = case_when(
      term1==term2 ~ NA_real_,
      TRUE ~ .value
    )
  ) %>% 
  filter(
    term1 != "PTHN × Levenshtein", 
    term2 != "Intercept"
  ) %>% 
  ggplot() +
  aes(
    fct_inorder(term1), 
    fct_rev(fct_inorder(term2)),
    fill = .value
  ) +
  geom_tile(na.rm = TRUE) +
  geom_text(
    aes(label = .value_label), 
    size = 3, 
    na.rm = TRUE
  ) +
  labs(
    x = "Term 1", 
    y = "Term 2", 
    fill = "Posterior\ncorrelation"
  ) +
  scale_fill_gradient2(
    low = "#04bf78", 
    mid = "white", 
    high = "#FFC20A", 
    na.value = "white", 
    limits = c(-0.4, 0.4)
  ) +
  scale_x_discrete(position = "top") +
  coord_equal() +
  theme(
    legend.position = c(1, 1),
    legend.direction = "horizontal",
    legend.key.height = unit(0.1, "cm"),
    legend.key.width = unit(0.4, "cm"),
    legend.justification = c(1, 1),
    legend.title = element_blank(),
    legend.text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0, vjust = 1),
    axis.text.y = element_text(size = 8, vjust = 1, hjust = 1)
  )

@@

```{r post_re_participant, echo=FALSE, fig.height=6, fig.width=9, message=FALSE, warning=FALSE, paged.print=FALSE}
post_re <- posterior_draws_random$participants %>% 
  mean_qi() %>% 
  ungroup() %>% 
  left_join(
    select(
      participants,
      participant_id,
      group
    )
  ) %>% 
  arrange(
    group, 
    participant_id, 
    .param
  ) %>% 
  mutate(
    .param_name = str_replace_all(
      .param, 
      str_repl
    ) %>%  
      factor(
        levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein"
        )
      )
  )

ggplot(
  post_re, 
  aes(
    .value, 
    sort(as.factor(participant_id)), 
    xmin = .lower,
    xmax = .upper,
    colour = group
  )
) +
  facet_grid(
    group~.param_name,
    scales = "free"
  ) +
  geom_vline(
    xintercept = 0, 
    colour = "grey"
  ) +
  geom_errorbarh(
    height = 0,
    alpha = 0.75
  ) +
  geom_point(
    size = 0.1,
    shape = 4
  ) +
  labs(
    x = "Participant-level adjustment",
    y = "Participant", 
    colour = "Group",
    title = "By participant"
  ) +
  scale_color_manual(
    values = c("#1A85FF", "#ff2976", "#FFC20A"),
    na.translate = FALSE
  ) &
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    panel.grid.major.x = element_line(
      colour = "grey",
      linetype = "dotted"
    ),
    axis.text.x = element_text(size = 7),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  )
```

```{r post_re_word, echo=FALSE, fig.height=9, fig.width=7, message=FALSE, warning=FALSE, paged.print=FALSE}
fixed_intercept <- fixef(fit_4)[1,c(1, 3, 4)] %>% 
  inv_logit_scaled()

empirical_accuracy <- responses %>% 
  group_by(group, translation_id, lv) %>% 
  summarise(
    successes = sum(correct, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    prop = prop_adj(successes, n),
    prop_se = prop_adj_se(successes, n)
  )

post_re <- posterior_draws_random$words %>% 
  ungroup() %>% 
  arrange(
    translation_id, 
    .param
  ) %>% 
  mutate(
    .param_name = str_replace_all(
      .param, 
      str_repl
    ) %>%  
      factor(
        levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein"
        )
      ),
    .value = inv_logit_scaled(.value)
  ) %>% 
  left_join(
    empirical_accuracy
  )

post_re %>% 
  left_join(
    select(
      stimuli,
      group,
      translation_id,
      translation,
      lv
    ) %>% 
      mutate(translation = paste0(translation, " (", percent(lv), ")"))
  ) %>% 
  ggplot(
    aes(
      x = .value,
      y = reorder(
        as.factor(translation), 
        .value
      )
    )
  ) +
  facet_wrap(
    ~group,
    scales = "free_y"
  ) +
  geom_vline(
    xintercept = fixed_intercept[1],
    colour = "grey", 
    size = 1
  ) +
  stat_interval(
    size = 1.5,
    .width = c(0.5, 0.67, 0.95)
  ) +
  geom_point(
    aes(
      x = prop
    ),
    size = 0.5,
    shape = 3
  ) +
  geom_errorbar(
    aes(
      x = prop,
      xmin = prop-prop_se,
      xmax = prop+prop_se
    ),
    width = 0,
    size = 0.5
  ) +
  labs(
    x = "Probability of correct response",
    y = "Translation",
    colour = "Model prediction (credible interval)",
    caption = "Credible intervals cover the range of values of the sampling space that contain the true value with a given certainty."
  ) +
  scale_color_manual(
    values = c("#d2e5fc", "#9ccaff", "#1A85FF"),
    na.translate = FALSE, 
    labels = paste0(c(95, 67, 50), "%")
  ) +
  scale_x_continuous(limits = c(0, 1), labels = percent) +
  theme(
    legend.position = "top",
    legend.key = element_rect(
      fill = NA, 
      colour = NA
    ),
    panel.grid.major.x = element_line(
      colour = "grey", 
      linetype = "dotted"
    ),
    axis.text.x = element_text(size = 7),
    axis.text.y = element_text(size = 5, hjust = 1),
    axis.ticks = element_blank(),
    axis.title = element_text(size = 10),
    plot.caption.position = "plot",
    plot.caption = element_text(
      size = 9, 
      hjust = 0, 
      face = "plain",
      margin = margin(t = unit(3, "cm"))
    )
  )

ggsave(
  here("img", "accuracy.png"), 
  height = 9,
  width = 14,
  dpi = 1000
)
```

```{r post_re_word_lv, echo=FALSE, fig.height=9, fig.width=7, message=FALSE, warning=FALSE, paged.print=FALSE}

fixed_intercept <- fixef(fit_4)[1,c(1, 3, 4)] %>% 
  inv_logit_scaled()

empirical_accuracy <- responses %>% 
  group_by(group, translation_id, lv) %>% 
  summarise(
    successes = sum(correct, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    prop = prop_adj(successes, n),
    prop_se = prop_adj_se(successes, n)
  )

post_re <- posterior_draws_random$words %>% 
  ungroup() %>% 
  arrange(
    translation_id, 
    .param
  ) %>% 
  mutate(
    .param_name = str_replace_all(
      .param, 
      str_repl
    ) %>%  
      factor(
        levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein"
        )
      ),
    .value = inv_logit_scaled(.value)
  ) %>% 
  left_join(
    empirical_accuracy
  )

post_re %>% 
  left_join(
    select(
      stimuli,
      group,
      translation_id,
      translation,
      lv
    ) %>% 
      mutate(translation = paste0(translation, " (", percent(lv), ")"))
  ) %>% 
  ggplot(
    aes(
      x = .value,
      y = reorder(
        as.factor(translation), 
        lv
      )
    )
  ) +
  facet_wrap(
    ~group,
    scales = "free_y"
  ) +
  geom_vline(
    xintercept = fixed_intercept[1],
    colour = "grey", 
    size = 1
  ) +
  stat_interval(
    size = 1.5,
    .width = c(0.5, 0.67, 0.95)
  ) +
  geom_point(
    aes(
      x = prop
    ),
    size = 0.5,
    shape = 4
  ) +
  geom_errorbar(
    aes(
      x = prop,
      xmin = prop-prop_se,
      xmax = prop+prop_se
    ),
    width = 0,
    size = 0.5
  ) +
  labs(
    x = "Posterior probability of correct response",
    y = "Translation (Levenshtein similarity)",
    colour = "Model prediction (credible interval)",
    caption = "Credible intervals cover the range of values of the sampling space that contain the true value with a given certainty."
  ) +
  scale_color_manual(
    values = c("#d2e5fc", "#9ccaff", "#1A85FF"),
    na.translate = FALSE, 
    labels = paste0(c(95, 67, 50), "%")
  ) +
  scale_x_continuous(limits = c(0, 1), labels = percent) +
  theme(
    legend.position = "top",
    legend.key = element_rect(
      fill = NA, 
      colour = NA
    ),
    panel.grid.major.x = element_line(
      colour = "grey", 
      linetype = "dotted"
    ),
    axis.text.x = element_text(size = 7),
    axis.text.y = element_text(size = 5, hjust = 1),
    axis.ticks = element_blank(),
    axis.title = element_text(size = 10),
    plot.caption.position = "plot",
    plot.caption = element_text(
      size = 9, 
      hjust = 0, 
      face = "plain",
      margin = margin(t = unit(3, "cm"))
    )
  )

ggsave(
  here("img", "accuracy_lv.png"), 
  height = 9,
  width = 16,
  dpi = 1000
)
```
